A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-07 latex/main.tex
Updates from Overleaf

% Multiple-breakpoint recombinants
% https://github.com/jeromekelleher/sc2ts-paper/issues/379

\begin{table}
\centering
\caption{
Sc2ts detection results for Pango X lineages not added to the ARG.
Some Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG absent in the ARG.
The number of samples in Viridian v04 dataset
assigned to a Pango X lineage and
the number of samples which passed sequence-level quality control
are shown here.
}
\label{tab:absent_pango_x}
\begin{tabular}{crrr}
\toprule
Pango & Samples in Viridian & Samples passing QC & Breakpoints \\
\midrule
XBJ & 2 & 1 & 1\\
XBP & 8 & 2 & 1\\
XBS & 19 & 15 & 1\\
XBW & 1 & 1 & 1\\
XCA & 11 & 4 & 1\\
XAK & 2 & 2 & 1\\   % Multiple breakpoint Pango X
XAY & 15 & 11 & 6\\ % Multiple breakpoint Pango X
XBC & 36 & 21 & 3\\ % Multiple breakpoint Pango X
XBL & 2 & 2 & 0\\   % Multiple breakpoint Pango X
XBT & 1 & 1 & 2\\   % Multiple breakpoint Pango X
\bottomrule
\end{tabular}
\end{table}

>>>>

% Multiple-breakpoint recombinants
% https://github.com/jeromekelleher/sc2ts-paper/issues/379
Ten Pango X lineages present in the Viridian v04 dataset
were not integrated into the ARG
due to high HMM costs and/or insufficient sample support,
but their samples were matched against the ARG during inference.
Table~\ref{tab:absent_pango_x} summarizes
the HMM matching results of these Pango X lineages.
All were identified as recombinants by sc2ts, except XBL
for which the evidence for recombination
supporting the suggested rightmost parent
involves only three informative sites,
which fall below our threshold of detection.
These results demonstrate that sc2ts can detect
recombinants with multiple breakpoints (XAY, XBC, and XBT).
The recombination patterns of these Pango X lineages
can be complex; exploring how to integrate such recombinants
should an important direction for future work.

\begin{table}
\centering
\caption{
Sc2ts detection results for Pango X lineages not added to the ARG.
The number of samples assigned to these Pango X lineages
in Viridian v04 dataset,
the number of samples which passed sequence-level quality control, and
the number of recombination breakpoints in the Viterbi solutions of the samples
are shown here.
}
\label{tab:absent_pango_x}
\begin{tabular}{crrr}
\toprule
Pango & Samples in Viridian & Samples passing QC & Breakpoints \\
\midrule
XBJ & 2 & 1 & 1\\
XBP & 8 & 2 & 1\\
XBS & 19 & 15 & 1\\
XBW & 1 & 1 & 1\\
XCA & 11 & 4 & 1\\
XAK & 2 & 2 & 1\\   % Multiple breakpoint Pango X
XAY & 15 & 11 & 6\\ % Multiple breakpoint Pango X
XBC & 36 & 21 & 3\\ % Multiple breakpoint Pango X
XBL & 2 & 2 & 0\\   % Multiple breakpoint Pango X
XBT & 1 & 1 & 2\\   % Multiple breakpoint Pango X
\bottomrule
\end{tabular}
\end{table}
